Automated topic naming to support analysis of software maintenance activities

### 2011-01-11 msr/msr2011.tex
Latest changes
some notes

\author{
\alignauthor 
Abram Hindle\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of California, Davis} \\
   \affaddr{Davis, CA, USA}\\
   \email{abram@softwareprocess.es}
\alignauthor  Neil A. Ernst\\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Department of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

Accordingly, we tried to associate each topic with a label from a list of keywords and related terms. 
We intersected the words of the topics and the words of our word-lists.
We `named' a topic if any of its words matched any of the word-list's words.
A topic could match more than one keyword.
We used several different sets of word-lists for comparison, which we refer to as \textsf{exp1, exp2, exp3} in the text which follows.

@@

\todo[inline]{* clarify the mailinglist stuff we did}
To construct these expanded word lists, we used WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words, including common related forms (similar to word stemming), meronymy and synonymy. 
We then added Boehm's 1976 software quality model \cite{Boehm+:1976:ICSE}, and classified his eleven `ilities' into their respective ISO9126 qualities. 
We did the same for the quality model produced by McCall et al. \cite{mccall1977}. 
Finally, we analyzed two mailing lists from another software project to expand our set with domain-specific terms. 
For example, we add the term ``performance'' to the synonyms for \emph{efficiency}, since this term occurs in most mail messages that discuss efficiency.

@@

% word list similarity
Using our three word lists, we labeled our topics where there was a match between a word in the list and the same word in the topic.
A \emph{named topic} is a topic with a matching label. 
There are roughly 20 times the number of topics as there are periods per project. 
This is because we told LDA to extract 20 topics per period. 
All experiments were run on MaxDB 7.500 and MySQL 3.23 data.
Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.

>>>>

\author{
\alignauthor 
Abram Hindle\\
   \affaddr{Dept.of Computer Science}\\
   \affaddr{University of California, Davis} \\
   \affaddr{Davis, CA, USA}\\
   \email{abram@softwareprocess.es}
\alignauthor  Neil A. Ernst\\
   \affaddr{Dept. of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{nernst@cs.toronto.edu}
\and
\alignauthor Michael W. Godfrey\\
   \affaddr{David Cheriton School of Computer Science}\\
   \affaddr{University of Waterloo}\\
   \affaddr{Waterloo, Ontario, CANADA}\\
   \email{migod@uwaterloo.ca}
\alignauthor John Mylopoulos \\
   \affaddr{Dept. of Computer Science}\\
   \affaddr{University of Toronto}\\
   \affaddr{Toronto, Ontario, CANADA}\\
   \email{jm@cs.toronto.edu}
}

@@

Accordingly, we tried to associate each topic with a label from a list
of keywords and related terms. These keywords were determined before
hand and were not extracted from the project themselves.
We intersected the words of the topics and the words of our word-lists.
We `named' a topic if any of its words matched any of the word-list's words.
A topic could match more than one keyword.
We used several different sets of word-lists for comparison, which we refer to as \textsf{exp1, exp2, exp3} in the text which follows.

@@

\todo[inline]{* clarify the mailinglist stuff we did}
\todo[inline]{This part doesn't make a lot of sense}
To construct these expanded word lists, we used WordNet~\cite{Fellbaum1998}, an English-language ``lexical database'' that contains semantic relations between words, including common related forms (similar to word stemming), meronymy and synonymy. 
We then added Boehm's 1976 software quality model \cite{Boehm+:1976:ICSE}, and classified his eleven `ilities' into their respective ISO9126 qualities. 
We did the same for the quality model produced by McCall et al. \cite{mccall1977}. 
Finally, we analyzed two mailing lists from another software project to expand our set with domain-specific terms. 
For example, we add the term ``performance'' to the synonyms for \emph{efficiency}, since this term occurs in most mail messages that discuss efficiency.

@@

% word list similarity
Using our three word lists (\textsf{exp1}, \textsf{exp2}, \textsf{exp3}), we labeled our topics where there was a match between a word in the list and the same word in the topic.
A \emph{named topic} is a topic with a matching label. 
There are roughly 20 times the number of topics as there are periods per project. 
This is because we told LDA to extract 20 topics per period. 
All experiments were run on MaxDB 7.500 and MySQL 3.23 data.
Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.
